Cosmic Microwave Background Power Spectra from Few Bit Timestreams

### 2018-09-17 digitisation.tex
Editing

Excellent observation conditions for CMB observations can be found at various locations on earth, including the South Pole \citep{kovac2007}, and in space. Space- and Antarctica-based experiments depend on satellite transmission. An experiment at the South Pole will be part of the next generation of ground-based instruments, which aims to collect 2 million detector years in total. Such an experiment will face a data influx of $\sim \mathcal{O}(10)\mathrm{Tb/d}$. However, the current transmission allocation for SPT3G is at $150\mathrm{Gb/d}$, which will likely see only a moderate increase in coming years. The transmission bottleneck is currently overcome by recovering the full data on hard drives with some latency and transmitting a downsampled version of the data. The downsampling process loses high frequency information. Continued use of downsampling will narrow the information window decisively - prohibiting high multipole moment science to be carried out on the transmitted data set. This also means that any potential faults or errors in the experiment visible in this range are not visible in the transmitted data. %C: Is there a paper detailing trasmission limits for SPT and that the data is currently downsampled?

The Planck mission has demonstrated the merits of carrying out CMB observations from space \citep{planck2018}. Upcoming missions aim to exceed the detector count of Planck by at least an order of magnitude \citep{litebird2014, pixie2011, core2018}. However, strategies to meet the telemetry specifications of each mission appear to be in development. It is not clear whether the data compression knowledge developed during the Planck mission will guarantee optimal performance for future satellites. Most likely each mission will have to carefully construct a compression algorithm through a combination of lossless and lossy techniques, specific to their requirements.

@@

Beyond transmission challenges, mission planning is becoming exceedingly difficult. Full simulation of TOD over the entire parameter space of detection scenarios is the desired way to decide on Stage-4 configurations. Given the shear size of TOD expected, this is not possible \citep{s4sciencebook}. Space-based missions carry out a similar analysis specific to their instruments to optimise their science output. Ground-based observations have to rely on different planning strategies or aim to reduce the size of the TOD in order to maximise the productivity of instruments.

@@

The Planck mission has demonstrated the advantages of using few bit compression of the CMB data \citep{maris2003}. Other science areas have also shown the power of extreme digtisation. \cite{jenet1998} explored the application of such compression to radio pulsar timing measurements with success. Recently Clearwater et al. (private communication) have investigated the advantages of using 1 and 2 bit data when searching for continuous gravitational waves using the Laser Interferometer Gravitational-Wave Observatory (LIGO).

@@

Digitisation is a lossy compression technique. However, the induced noise depends on the details of the digitisation scheme. To minimise the noise induced through this process one must know the nature of the input signal. There is usually little concern around finding an optimal set of digitisation parameters for an input signal as it is common to have access to large numbers of bits to store information, where changes in the digitisation scheme become insignificant to the distortion induced. It is in our interest however to consider extreme, i.e. few-bit, digitisation. In this case the digitisation scheme must be carefully constructed. We review the key of digitisation as edtablished by \cite{max1960} below.

@@

We use the findings of \cite{max1960} to formulate the multi-level functions we use for our 1, 2 and 3 bit digitisation process. Given an input signal $s(t)$ a digitisation scheme using $N$ bits returns the output $\hat{s}_N(t)$. For 1 bit digitisation we apply the sign function

@@

Having constructed I,Q and U TOD we apply the digitisation schemes derived above. We compress the timestreams into maps by averaging all hits falling into the same pixel. We produce 24 CMB maps in total: three control maps and nine maps with three each obtained from the different digitisation schemes. We simulate six observations, producing maps with $800$, $8,000$, $80,000$, $1,024,000$, $10,240,000$ and $102,400,000$ hits in each pixel.

@@

We use the Spatially Inhomogeneous Correlation Estimator for Temperature and Polarisation \citep[PolSpice;][]{polspice} to compute $\mathrm{TT}, \mathrm{EE}$ and $\mathrm{BB}$ power spectra. To minimise cut sky effects we apodise the observed path using a cosine mask with $\sigma_{\mathrm{APOD}} = \sqrt{600}/2 \hspace{0.7ex} \mathrm{deg}$. %C: Should I also mention the multiplication with a cosine mask that I supply in addition to setting this option on polspice? This will likely be reworked when using Healpix to get the power spectra though.

@@

To investigate whether the noise added through digitisation has any $\ell$ dependence we subtract the template maps from the simulated observations. We use theoretically calculated normalisation constants to minimise calibration error. The power spectra of the difference maps do not show any $\ell$ dependence in the added noise as seen in figure \ref{fig:diffpswn}. % This is in agreement with (planck website) but does not match the results of (planck short paper). This is likely due to the intricities of the planck compression scheme differing to what is considered here. A full comparison is difficult in the absense of a detailed description of the simulations carried out in either paper.

@@

Before analysing $C_\ell^\mathrm{X}/C_\ell^\mathrm{N}$ we rebin the power spectra to $\Delta \ell \approx 100$. This guarantees that the points in the noise tail are independent of one another, allowing us to extract an uncertainty for the above quantity.

The deduced additional noise for 1, 2 and 3 bit digitisation schemes are shown in table \ref{tab:extranoisewhite} in the appendix. As expected 3 Bit digitisation performs the best, followed by 2 Bit and finally 1 Bit digitisation. This i because with each additional bit we retain more information. We observe that $\Delta \sigma / \sigma$ is independent of the hits per pixel in the maps. This suggests that the additional noise scales in the same way as detector noise does. Furthermore, the compression works equally well for temperature as it does for polarisation observations. Lastly, the added noise levels are low. The optimal 3 Bit digitisaiton scheme devised adds as little as $1.8\%$ to the map noise level. Keeping in mind that CMB detector sensitivity improves in steps of order of magnitude every few years, adding an extra percent-level noise term does not deteriorate the results appreciably. This is impressive, given that the use of an optimal 3 bit digitisation scheme reduces TOD volume by an order of magnitude.

@@

We follow up on the compelling results of the white noise case by implementing a more realistic noise profile. Noise profiles of ground-based CMB observations have prominent $1/f$ character due to atmospheric effects \citep{lay2000}. We use the Fourier space noise profile

@@

where the first term on the second line produces $1/f$ behaviour and the second term on the same line suppressed the lowest modes. For temperature observations we choose $\lknee = 1000$ and $\lcut = 336$, to ensure that $|N_{1/f}(0.3\lknee)|^2 = |0.95 \sigma|^2$. For polarisation we set $\lknee = 50$ and $\lcut = 17$ for the same reason.

@@

We recover similar results to the white noise case. As before 3 bit performs the best, followed by 2 bit and 1 bit. The excess noise due to digitisation does not show any $\ell$ dependence. The noise contribution to the map noise level from digitisation for $1/f$ noise is the same as for white noise and does not vary with the number of hits per pixel in the map. Temperature and polarisation observations incur the same distortion. Table \ref{tab:extranoiseoof} in the appendix displays the values of $\Delta \sigma / \sigma$ calculated.

@@

We derived a set of 1, 2 and 3 bit digitisation schemes assuming white detector noise. Through simulated observation we determined the distortion this compression technique causes in temperate and polarisation power spectra. We find that an optimal 3 bit digitisation adds as little as $1.8\%$ to the map noise level for temperature and polarisation observations alike. No change in the results is observed for maps of different hits per pixel and no $\ell$ dependence was observed in the added noise. Extending the model to more realistic $1/f$ detector noise did not change these results.

@@

\def\arraystretch{1.3}
\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:extranoisewhite} Additional Noise - White Detector Noise}
\small
\begin{tabular}{c c c c c}
Hits Per Pixel & Channel & 1 Bit & 2 Bit & 3 Bit \\
\hline
\hline
\multirow{3}{*}{$800$}  & TT  & $ 0.252 \pm 0.009 $  & $ 0.064 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.012 $  & $ 0.064 \pm 0.005 $  & $ 0.017 \pm 0.004 $ \\
& BB  & $ 0.252 \pm 0.011 $  & $ 0.066 \pm 0.005 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$8,000$}  & TT  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.004 $  & $ 0.017 \pm 0.002 $ \\
& BB  & $ 0.25 \pm 0.018 $  & $ 0.064 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$80,000$}  & TT  & $ 0.249 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& EE  & $ 0.25 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.247 \pm 0.018 $  & $ 0.064 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$1,024,000$}  & TT  & $ 0.25 \pm 0.009 $  & $ 0.063 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.008 $  & $ 0.065 \pm 0.003 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.251 \pm 0.008 $  & $ 0.064 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
\hline
\multirow{3}{*}{$10,240,000$}  & TT  & $ 0.186 \pm 0.025 $  & $ 0.047 \pm 0.007 $  & $ 0.013 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.009 $  & $ 0.064 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.25 \pm 0.012 $  & $ 0.065 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
\hline
\multirow{3}{*}{$102,400,000$}  & TT  & $ 0.246 \pm 0.004 $  & $ 0.063 \pm 0.002 $  & $ 0.017 \pm 0.001 $ \\
& EE  & $ 0.251 \pm 0.008 $  & $ 0.064 \pm 0.004 $  & $ 0.017 \pm 0.002 $ \\
& BB  & $ 0.251 \pm 0.009 $  & $ 0.065 \pm 0.003 $  & $ 0.018 \pm 0.002 $ \\
\end{tabular}
\tablecomments{ 
Percent addition to the map noise level $\Delta \sigma / \sigma$ by digitisation. Notice the invariance for each digitisation scheme with the number of hits per pixel and channel.
} \normalsize
\end{center}
\end{table*}

\def\arraystretch{1.3}
\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:extranoiseoof} Additional Noise - $1/f$ Detector Noise}
\small
\begin{tabular}{c c c c c}
Hits Per Pixel & Channel & 1 Bit & 2 Bit & 3 Bit \\
\hline
\hline
\multirow{3}{*}{$8,000$}  & TT  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.004 $  & $ 0.017 \pm 0.002 $ \\
& BB  & $ 0.25 \pm 0.018 $  & $ 0.064 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$102,400$}  & TT  & $ 0.249 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& EE  & $ 0.25 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.247 \pm 0.018 $  & $ 0.064 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$1,024,000$}  & TT  & $ 0.25 \pm 0.009 $  & $ 0.063 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.008 $  & $ 0.065 \pm 0.003 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.251 \pm 0.008 $  & $ 0.064 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
\end{tabular}
\tablecomments{ 
Percent addition to the map noise level $\Delta \sigma / \sigma$ by digitisation. Notice the invariance for each digitisation scheme with the number of hits per pixel and channel.
} \normalsize
\end{center}
\end{table*}

>>>>

Excellent observation conditions for CMB observations can be found in space and at various locations on earth, including the South Pole \citep{kovac2007}. Space- and Antarctica-based experiments depend on satellite transmission. The South Pole will continue its contribution to CMB science in the next generation of ground-based instruments, which aims to collect 2 million detector years in total. During Stage-4 operation the Sout Pole site will face a data influx of $\sim \mathcal{O}(10)\mathrm{Tb/d}$. However, the current transmission allocation for SPT3G is at $150\mathrm{Gb/d}$, which will likely see only a moderate increase. The transmission bottleneck is currently overcome by recovering the full data on hard drives with some latency and transmitting a downsampled version of the data. The downsampling process loses high frequency information and continued usage of it will narrow the information window decisively - prohibiting high multipole moment science to be carried out on the transmitted data set. This also means that any potential faults or errors in the experiment apparent in this range are not visible in the transmitted data. %C: Is there a paper detailing trasmission limits for SPT and that the data is currently downsampled?

The Planck mission has demonstrated the merits of carrying out CMB observations from space \citep{planck2018}. Upcoming missions aim to exceed the detector count of Planck by at least an order of magnitude \citep{litebird2014, pixie2011, core2018}. Strategies to meet the telemetry specifications of each mission appear to be in development. It is not clear whether the data compression knowledge developed during the Planck mission will guarantee optimal performance for future satellites. Most likely each mission will have to carefully construct a compression algorithm through a combination of lossless and lossy techniques, specific to their requirements.

@@

Beyond transmission challenges, mission planning is becoming exceedingly difficult. Full simulation of TOD over the entire parameter space of detection scenarios is the desired way to decide on Stage-4 configurations. Given the shear size of TOD expected, this is not possible \citep{s4sciencebook}. Space-based missions carry out a similar analysis specific to their instruments to optimise their science output. Ground-based observations have to rely on different planning strategies or aim to reduce the size of the TOD in order to maximise the productivity of the design stage.

@@

The Planck mission has demonstrated the advantages of using few bit CMB data \citep{maris2003}. Other science areas have also shown the power of extreme digtisation. \cite{jenet1998} explored the application of such compression to radio pulsar timing measurements with success. Recently Clearwater et al. (private communication) have demonstrated the advantages of using 1 and 2 bit data when searching for continuous gravitational waves using the Laser Interferometer Gravitational-Wave Observatory (LIGO).

@@

Digitisation is a lossy compression technique. However, the additional noise depends on the details of the digitisation scheme. To minimise distortion knowledge of the input signal is essential. There is usually little concern around finding an optimal set of digitisation parameters for an input signal as it is common to have access to large numbers of bits to store information, where changes in the digitisation scheme become insignificant to the distortion induced. It is in our interest however to consider extreme, i.e. few-bit, digitisation. In this case the digitisation scheme must be carefully constructed. We review the key aspedcts of designing digitisation schemes as edtablished by \cite{max1960} below.

@@

We use the findings of \cite{max1960} to formulate the multi-level functions we use for 1, 2 and 3 bit digitisation. Given an input signal $s(t)$ a digitisation scheme using $N$ bits returns the output $\hat{s}_N(t)$. For 1 bit digitisation we apply the sign function

@@

Having constructed I,Q and U TOD we apply the digitisation schemes derived above. We compress the timestreams into maps by averaging all hits falling into the same pixel. We produce 24 CMB maps in total: three control maps and nine maps with three each obtained from the different digitisation schemes. We simulate six observations with $800$, $8,000$, $80,000$, $1,024,000$, $10,240,000$ and $102,400,000$ hits per map pixel.

@@

We use the Spatially Inhomogeneous Correlation Estimator for Temperature and Polarisation \citep[PolSpice;][]{polspice} to compute $\mathrm{TT}$, $\mathrm{EE}$ and $\mathrm{BB}$ power spectra. To minimise cut sky effects we apodise the observed path using a cosine mask with $\sigma_{\mathrm{APOD}} = \sqrt{600}/2 \hspace{0.7ex} \mathrm{deg}$. %C: Should I also mention the multiplication with a cosine mask that I supply in addition to setting this option on polspice? This will likely be reworked when using Healpix to get the power spectra though.

@@

To investigate whether the noise added through digitisation has any $\ell$ dependence we subtract the template maps from the simulated observations. Beyond a calibration error, the power spectra of the difference maps do not show any $\ell$ dependence in the added noise as seen in figure \ref{fig:diffpswn}. % This is in agreement with (planck website) but does not match the results of (planck short paper). This is likely due to the intricities of the planck compression scheme differing to what is considered here. A full comparison is difficult in the absense of a detailed description of the simulations carried out in either paper.

@@

Before analysing $C_\ell^\mathrm{X}/C_\ell^\mathrm{N}$ we rebin the power spectra to $\Delta \ell \approx 100$. This ensures that the points in the noise tail are independent of one another, allowing us to extract an uncertainty for the above quantity.

The deduced additional noise for 1, 2 and 3 bit digitisation schemes is shown in table \ref{tab:extranoisewhite} in the appendix. As expected 3 Bit digitisation performs the best, followed by 2 Bit and finally 1 Bit digitisation. This is because with each additional bit we retain more information. We observe that $\Delta \sigma / \sigma$ is independent of the hits per pixel in the maps. This suggests that the additional noise scales in the same way as detector noise does. Furthermore, the compression works equally well for temperature as it does for polarisation observations. Lastly, the added noise levels are low. The optimal 3 Bit digitisaiton scheme devised adds as little as $1.7\%$ to the map noise level. Keeping in mind that CMB detector sensitivity improves in steps of order of magnitude every few years, adding an extra percent-level noise term does not deteriorate the results appreciably. This is impressive, given that the use of an optimal 3 bit digitisation scheme reduces TOD volume by an order of magnitude.

@@

We follow up on the compelling results of the white noise case by implementing a more realistic noise profile. Ground-based CMB observations have $1/f$ noise spectra due to atmospheric effects \citep{lay2000}. We use the Fourier space noise profile

@@

where $N\left(0, \sigma \right)$ denotes a normally distributed random variable with mean $0$ and standard deviation $\sigma$. the first term on the second line produces $1/f$ behaviour and the second term on the same line suppressed the lowest modes. For temperature observations we choose $\lknee = 1000$ and $\lcut = 336$, to ensure that $|N_{1/f}(0.3\lknee)|^2 = |0.95 \sigma|^2$. For polarisation we set $\lknee = 50$ and $\lcut = 17$ for the same reason.

@@

We recover similar results to the white noise case. As before 3 bit performs the best, followed by 2 bit and 1 bit. The excess noise due to digitisation does not show any $\ell$ dependence. The noise contribution to the map noise level from digitisation for $1/f$ noise is the same as for white noise and does not vary with the number of hits per pixel in the map. Temperature and polarisation observations incur the same noise penalty. Table \ref{tab:extranoiseoof} in the appendix displays the values of $\Delta \sigma / \sigma$ calculated.

@@

We derived a set of 1, 2 and 3 bit digitisation schemes assuming white detector noise. Through simulated observation we determined the distortion this compression technique causes in temperate and polarisation power spectra. We find that an optimal 3 bit digitisation adds as little as $1.7\%$ to the map noise level for temperature and polarisation observations alike. No change in the results is observed for maps of different hits per pixel and no $\ell$ dependence was observed in the added noise. Extending the model to more realistic $1/f$ detector noise did not change these results.

@@

\def\arraystretch{1.3}
\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:extranoisewhite} Additional Noise - White Detector Noise}
\small
\begin{tabular}{c c c c c}
Hits Per Pixel & Channel & 1 Bit & 2 Bit & 3 Bit \\
\hline
\hline
\multirow{3}{*}{800}  & TT  & $ 0.252 \pm 0.009 $  & $ 0.064 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.253 \pm 0.012 $  & $ 0.064 \pm 0.005 $  & $ 0.017 \pm 0.004 $ \\
& BB  & $ 0.254 \pm 0.011 $  & $ 0.065 \pm 0.005 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{8000}  & TT  & $ 0.252 \pm 0.008 $  & $ 0.064 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.004 $  & $ 0.017 \pm 0.002 $ \\
& BB  & $ 0.252 \pm 0.018 $  & $ 0.063 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{80000}  & TT  & $ 0.249 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& EE  & $ 0.25 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.248 \pm 0.018 $  & $ 0.063 \pm 0.009 $  & $ 0.018 \pm 0.003 $ \\
\hline
\multirow{3}{*}{1024000}  & TT  & $ 0.25 \pm 0.009 $  & $ 0.063 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.008 $  & $ 0.065 \pm 0.003 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.252 \pm 0.008 $  & $ 0.064 \pm 0.004 $  & $ 0.017 \pm 0.002 $ \\
\hline
\multirow{3}{*}{10240000}  & TT  & $ 0.186 \pm 0.025 $  & $ 0.046 \pm 0.007 $  & $ 0.013 \pm 0.002 $ \\
& EE  & $ 0.253 \pm 0.009 $  & $ 0.065 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.252 \pm 0.012 $  & $ 0.064 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
\hline
\multirow{3}{*}{102400000}  & TT  & $ 0.246 \pm 0.005 $  & $ 0.063 \pm 0.002 $  & $ 0.017 \pm 0.001 $ \\
& EE  & $ 0.251 \pm 0.008 $  & $ 0.064 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.252 \pm 0.009 $  & $ 0.064 \pm 0.003 $  & $ 0.018 \pm 0.002 $ \\
\hline
\multicolumn{2}{c}{Average}  & $ 0.248 \pm 0.011 $  & $ 0.063 \pm 0.005 $  & $ 0.017 \pm 0.002 $ \\
\end{tabular}
\tablecomments{ 
Percent addition to the map noise level $\Delta \sigma / \sigma$ by digitisation for white detector noise. Notice the invariance for each digitisation scheme with the number of hits per pixel and channel.
} \normalsize
\end{center}
\end{table*}

\def\arraystretch{1.3}
\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:extranoiseoof} Additional Noise - $1/f$ Detector Noise}
\small
\begin{tabular}{c c c c c}
Hits Per Pixel & Channel & 1 Bit & 2 Bit & 3 Bit \\
\hline
\hline
\multirow{3}{*}{$8,000$}  & TT  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.007 $  & $ 0.064 \pm 0.004 $  & $ 0.017 \pm 0.002 $ \\
& BB  & $ 0.25 \pm 0.018 $  & $ 0.064 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$102,400$}  & TT  & $ 0.249 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& EE  & $ 0.25 \pm 0.011 $  & $ 0.064 \pm 0.005 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.247 \pm 0.018 $  & $ 0.064 \pm 0.009 $  & $ 0.018 \pm 0.004 $ \\
\hline
\multirow{3}{*}{$1,024,000$}  & TT  & $ 0.25 \pm 0.009 $  & $ 0.063 \pm 0.003 $  & $ 0.017 \pm 0.002 $ \\
& EE  & $ 0.252 \pm 0.008 $  & $ 0.065 \pm 0.003 $  & $ 0.018 \pm 0.002 $ \\
& BB  & $ 0.251 \pm 0.008 $  & $ 0.064 \pm 0.004 $  & $ 0.018 \pm 0.002 $ \\
\hline
\multicolumn{2}{c}{Average}  & $ 0.248 \pm 0.011 $  & $ 0.063 \pm 0.005 $  & $ 0.017 \pm 0.002 $ \\
\end{tabular}
\tablecomments{ 
Percent addition to the map noise level $\Delta \sigma / \sigma$ by digitisation for $1/f$ detector noise. The invariance with depth of observation and channel as well as the values match the white noise case.
} \normalsize
\end{center}
\end{table*}
